Software Clusterings with Vector Semantics and the Call Graph

### 2019-06-25 manuscript/manuscript.tex
Remove review template and concatenated abstract

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf,review, anonymous]{acmart}
\usepackage{float}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

@@

\email{papachristoumarios@gmail.com}
\affiliation{%
  \institution{National Technical University of Athens}
  \streetaddress{Zografou Campus}
  \city{Athens}
  \state{Attica}
  \postcode{157 73}
}

@@

\noindent \textbf{Purpose -- } Propose a novel method to determine a software's modules without 
knowledge of its architectural structure, and empirically validate the method's performance.

\noindent \textbf{Method -- } Cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph.
Use of the \emph{Louvain Algorithm} to determine its community structure and propose a module--level clustering.

\noindent \textbf{Results --} Our method performs better in terms of stability, authoritativeness 
and extremity over other state-of-the-art clustering methods proposed in literature and is able to decently 
recover the ground truth clustering of the Linux Kernel.

\noindent \textbf{Conclusions and Contributions --} Semantic information from vector semantics as well as the call graph can produce 
accurate results for software clusterings of large systems.

>>>>

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
\usepackage{float}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

@@

\email{papachristoumarios@gmail.com}
\additionalaffiliation{%
  \institution{Business Analytics Lab at Athens University of Economics and Business}
  \streetaddress{Patision Campus}
  \city{Athens}
  \state{Attica}
  \postcode{104 34}
}
\affiliation{%
  \institution{National Technical University of Athens}
  \streetaddress{Zografou Campus}
  \city{Athens}
  \state{Attica}
  \postcode{157 73}
}

@@

In this paper, we propose a novel method to determine a software's modules without 
knowledge of its architectural structure, and empirically validate the method's performance. We cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph. Use of the \emph{Louvain Algorithm} to determine its community structure and propose a module--level clustering. 
Our method performs better in terms of stability, authoritativeness 
and extremity over other state-of-the-art clustering methods proposed in literature and is able to decently 
recover the ground truth clustering of the Linux Kernel. 
Finally, we conclude that semantic information from vector semantics as well as the call graph can produce 
accurate results for software clusterings of large systems.
